### 2017-06-28 paper/oopsla17-submission/qualitative.tex

Our top prediction coincides with \sherrloc (and \ocaml), blaming the
the first argument to |clone| rather than the occurrence of |clone| itself.
%
% This is also incorrect, but may be more helpful than our first
% prediction --- if our student decides that she has certainly provided
% the correct \emph{argument}, an alternative explanation is that
% perhaps she has called the wrong \emph{function}.
%
We confess that this prediction is difficult to explain by
examining the induced paths.
%
In particular, it only references the expression's context,
which is surprising.
%
Much clearer is why we fail to blame the occurrence of |clone|, the two
enabled features on the path are:
%
(1) the parent is an application; and
%
(2) |clone| has a function type.
%
The model seems to have learned that programmers typically call the
correct function.

\mypara{Currying Considered Harmful?}
% data/sp14/1080.ml
Our next example is another ill-fated attempt at |clone|.
%
\begin{ecode}
  let rec clone x n =
    let rec loop (*@\hlFix{x n acc}@*) =
      if n < 0 then
        acc
      else
        (*@\hlSherrloc{loop} \hlTree{(x, (n - 1), (x :: acc))}@*) in
    loop (x, n, [])
\end{ecode}
%
The issue here is that \ocaml functions are \emph{curried} by default
--- \ie they take their arguments one at a time --- but our student has
called the inner |loop| with all three arguments in a tuple.
%
Many experienced functional programmers would choose to keep |loop|
curried and rewrite the calls, however our student decides instead to
\emph{uncurry} |loop|, making it take a tuple of arguments.
%
\sherrloc blames the recursive call to |loop| while our classifier
blames the tuple of arguments --- a reasonable suggestion, but not
the answer the student expected.

@@

As our \dectree correctly points out (with high confidence), the fault
lies with the list literal \emph{surrounding} the recursive call, remove
it and the type error disappears.
%
An examination of the path induced by the list literal reveals that our
\dectree is basing its decision on the fact that
%
(1) the expression is a list literal;
%
(2) the child expression is an application, whose return type mentions |int|; and
%
(3) the parent expression's type mentions |list|.
%
Interestingly, \dectree incorrectly predicts that the child application
should change as well, but it is less confident of this prediction and
ranks it below the correct blame assignment.

@@

Our \dectree correctly predicts that the recursive call blamed by
\sherrloc should not be blamed; a similar examination suggests that the
crucial observation is that the recursive call's parent is a data
constructor application.
%

>>>>

Our top prediction coincides with \sherrloc (and \ocaml), blaming the
the first argument to |clone| rather than the occurrence of |clone| itself.
%
% This is also incorrect, but may be more helpful than our first
% prediction --- if our student decides that she has certainly provided
% the correct \emph{argument}, an alternative explanation is that
% perhaps she has called the wrong \emph{function}.
%
We confess that this prediction is difficult to explain by
examining the induced paths.
%
In particular, it only references the expression's context,
which is surprising.
%
More clear is why we fail to blame the occurrence of |clone|, two of
the enabled features on the path are:
%
(1) the parent is an application; and
%
(2) |clone| has a function type.
%
The model appears to have learned that programmers typically call the
correct function.

\mypara{Currying Considered Harmful?}
% data/sp14/1080.ml
Our next example is another ill-fated attempt at |clone|.
%
\begin{ecode}
  let rec clone x n =
    let rec loop (*@\hlFix{x n acc}@*) =
      if n < 0 then
        acc
      else
        (*@\hlSherrloc{loop} \hlTree{(x, (n - 1), (x :: acc))}@*) in
    loop (x, n, [])
\end{ecode}
%
The issue here is that \ocaml functions are \emph{curried} by default
--- \ie they take their arguments one at a time --- but our student has
called the inner |loop| with all three arguments in a tuple.
%
Many experienced functional programmers would choose to keep |loop|
curried and rewrite the calls, however our student decides instead to
\emph{uncurry} |loop|, making it take a tuple of arguments.
%
\sherrloc blames the recursive call to |loop| while our classifier
blames the
% third element of the tuple.
tuple of arguments --- a reasonable suggestion, but not
the answer the student expected.

@@

As our \dectree correctly points out (with high confidence), the fault
lies with the list literal \emph{surrounding} the recursive call, remove
it and the type error disappears.
%
An examination of the path induced by the list literal reveals that our
\dectree is basing its decision on the fact that
%
(1) the expression is a list literal;
%
(2) the child expression is an application, whose return type mentions |int|; and
%
(3) the parent expression is also an application.
%
Interestingly, \dectree incorrectly predicts that the child application
should change as well, but it is less confident of this prediction and
ranks it below the correct blame assignment.

@@

Our \dectree correctly predicts that the recursive call blamed by
\sherrloc should not be blamed; a similar examination suggests that the
crucial observation is that the recursive call's parent is a data
constructor application.
